Preregistered as Code: Gender differences in Machiavellianism

### 2021-08-06 manuscript.Rmd
link hash closes #207
update repro closes #211

    - aaronpeikert/repro@c3cae1f

@@

Once the R Markdown file has been rendered to a static document, the resulting file is decoupled from the R Markdown and the code that created it.
This introduces a risk that multiple versions of the static document are disseminated, each with slightly different results.
To avoid ambiguity, we therefore recommend referencing the identifier of the Git commit at the time of rendering in the static document.
Simply put, a static document should link to the version of the code that was used to create it.
The `repro` package comes with the function `repro::current_hash()` for this purpose.
This document was created from the commit with the hash ``r repro::current_hash()``.

@@

The function `planned_analysis()` together with the function `simulate_data()` (not shown here) can be used to justify the planned sample size.
To that end, `simulate_data()` is repeatedly called with increased sample size and the proportion of significant results (power) is recorded.
The results for such a Monte Carlo simulation for this example are visualized in figure \@ref(fig:power).
The code for this power analysis can be found in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R).

@@

```{r, echo=FALSE, results='asis'}
show_prereg("power-code", wrap = FALSE)
```

>>>>

    - aaronpeikert/repro@27e7d22

@@

Once the R Markdown file has been rendered to a static document, the resulting file is decoupled from the R Markdown and the code that created it.
This introduces a risk that multiple versions of the static document are disseminated, each with slightly different results.
To avoid ambiguity, we therefore recommend referencing the identifier of the Git commit at the time of rendering in the static document.
Simply put, a static document should link to the version of the code that was used to create it.
The `repro` package comes with the function `repro::current_hash()` for this purpose.
This document was created from the commit with the hash [``r repro::current_hash()``](`r stringr::str_c("https://github.com/aaronpeikert/repro-tutorial/tree/", repro::current_hash(40))`).

@@

The function `planned_analysis()` together with the function `simulate_data()` (not shown here) can be used to justify the planned sample size.
To that end, `simulate_data()` is repeatedly called with increased sample size and the proportion of significant results (power) is recorded.
The results for such a Monte Carlo simulation for this example are visualized in figure \@ref(fig:power).
The code for this power analysis can be found in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R).
The next snippet shows how we included the results dynamically into the preregistration (the origin of the R-variables `minn`, `choosen_power`, and `choosen_d` is not shown).

@@

### 2021-08-06 preregistration.Rmd
update repro closes #211

<!--begin-ttest-->
We conduct a Student's t-test [@studentProbableErrorMean1908] with Welch's correction [@welchGeneralizationStudentProblem1947] of the average of machiavellianism items between the binary-coded gender groups.
If the skew of this average is greater than 1.0 we conduct a supposedly more robust Mann--Whitney--Wilcoxon test [@Wilcoxon1945] instead.
<!--end-ttest-->
<!--begin-power-code-->
```{r, echo=FALSE}
choosen_power <- .8
choosen_d <- .2
minn <-
  filter(filter(simulation_results, d == choosen_d, power > choosen_power),
         n == min(n))$n
```
<!--end-power-code-->
<!--begin-power-->
A simulation we conducted indicated that with a sample size of
`r minn` for an alpha of .05 (two-sided) we achieve at least `r choosen_power*100`% power assuming a standardized effect size of d=`r choosen_d`.
<!--end-power-->

>>>>

<!--begin-ttest-->
We conduct a Student's t-test [@studentProbableErrorMean1908] with Welch's correction [@welchGeneralizationStudentProblem1947] of the average of machiavellianism items between the binary-coded gender groups.
If the skew of this average is greater than 1.0 we conduct a supposedly more robust Mann--Whitney--Wilcoxon test [@Wilcoxon1945] instead.
<!--end-ttest-->
```{r, echo=FALSE}
choosen_power <- .8
choosen_d <- .2
minn <-
  filter(filter(simulation_results, d == choosen_d, power > choosen_power),
         n == min(n))$n
```
<!--begin-power-->
A simulation we conducted indicated that with a sample size of
`r minn` for an alpha of .05 (two-sided) we achieve at least `r choosen_power*100`% power assuming a standardized effect size of d=`r choosen_d`.
<!--end-power-->
